### 2016-05-18 writing/presentation/coincidences.tex
Anders chap3/4

\subsection{Summary of Experimental Results}
\label{sub:Summary of Experimental Results}
\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Second Dominating rule}&\(59\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Third Dominating rule}&\(56\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
    \label{tab:domclasses}
\end{table}
\end{block}
\end{frame}

@@

@@

@@

>>>>

\subsection{Summary of Experimental Results}
\label{sub:Summary of Experimental Results}
\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{First Dominating rule}}&\hspace{0pt}\invisible<2->{\(85\)}&\hspace{0pt}\invisible<2->{\(43\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{Second Dominating rule}}&\hspace{0pt}\invisible<2->{\(59\)}&\hspace{0pt}\invisible<2->{\(39\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible<2->{Third Dominating rule}}&\hspace{0pt}\invisible<2->{\(56\)}&\hspace{0pt}\hspace{0pt}\invisible<2->{\(39\)}&\hspace{0pt}\invisible<2->{\(220\)}&\hspace{0pt}\hspace{0pt}\invisible<2->{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
    \label{tab:domclasses}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Second Dominating rule}}&\hspace{0pt}\invisible{\(59\)}&\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Third Dominating rule}}&\hspace{0pt}\invisible{\(56\)}&\hspace{0pt}\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Second Dominating rule}&\(59\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{\hspace{0pt}\invisible{Third Dominating rule}}&\hspace{0pt}\invisible{\(56\)}&\hspace{0pt}\invisible{\(39\)}&\hspace{0pt}\invisible{\(220\)}&\hspace{0pt}\invisible{\(29\)}\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}

@@

\begin{frame}{Experimental Results}
  \begin{block}{}
  \begin{table}[htb]
\begin{center}
\begin{tabularx}{\textwidth}{c|Y|Y|Y|Y|}
\cline{2-5}
& \multicolumn{4}{|c|}{Dominating Pattern}\\
\cline{2-5}
& \multicolumn{2}{|c|}{\(\perm{2,3,1}\)}&\multicolumn{2}{|c|}{\(\perm{3,2,1}\)}\\
\cline{2-5}
& \(\perm{1,2}\)&\(\perm{2,1}\)&\(\perm{1,2}\)&\(\perm{2,1}\)\\
\hline
\multicolumn{1}{|r|}{No Dominating rule}&\(220\)&\(220\)&\(220\)&\(220\)\\
\hline
\multicolumn{1}{|r|}{First Dominating rule}&\(85\)&\(43\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Second Dominating rule}&\(59\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Third Dominating rule}&\(56\)&\(39\)&\(220\)&\(29\)\\
\hline
\multicolumn{1}{|r|}{Experimental class size}&\(56\)&\(39\)&\(213\)&\(29\)\\
\hline
\end{tabularx}
\end{center}
    \caption{Coincidence class number reduction by application of Dominating rules}
\end{table}
\end{block}
\end{frame}
